Stable individual differences in strategies within, but not between, visual search tasks

### 2019-10-22 Manuscript/manuscript.tex

The display was presented on a 17-inch CRT monitor with a resolution of $1400 \times 1050$ ($n = 40$) or $1600 \times 1200$ ($n = 24$). Stimulus generation, presentation and data collection were controlled by MATLAB and the psychophysics and eyelink toolboxes  \cite{brainard1997,cornelissen2002} run on a Powermac. Participants sat $\approx 47$cm from the screen.

>>>>

The display was presented on a 17-inch CRT monitor with a resolution of $1400 \times 1050$ ($n = 40$) or $1600 \times 1200$ ($n = 24$). Stimulus generation, presentation and data collection were controlled by MATLAB and the psychophysics and eyelink toolboxes  \cite{brainard1997,cornelissen2002,kleiners2007} run on a Powermac. Participants sat $\approx 47$cm from the screen.
